%% using aastex version 6.3
\documentclass[twocolumn, linenumbers, tighten]{aastex631}
\usepackage{float}
\usepackage[T1]{fontenc} % Ensures proper encoding
\usepackage[utf8]{inputenc} % Enables UTF-8 encoding

% old: A&A 
%\documentclass{aa}

\usepackage{nameref}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{cuted}
%\usepackage[varg]{txfonts}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}

\usepackage{longtable}
%\usepackage{caption}


% Croatian letter "dj"
\def\d   {{d $\mkern-14.3mu \mathchar'26 $}}


\begin{document}
\title{Search for the Blazhko effect in field RR Lyrae stars using LINEAR and ZTF light curves}

\author{Ema Donev}
\affiliation{XV. Gymnasium (MIOC), Jordanovac 8, 10000, Zagreb, Croatia}

\author[0000-0001-5250-2633]{\v{Z}eljko Ivezi\'{c}}
\affiliation{Department of Astronomy and the DiRAC Institute, University of Washington, 3910 15th Avenue NE, Seattle, WA 98195, USA}

\correspondingauthor{\v{Z}eljko Ivezi\'{c}}
\email{ivezic@uw.edu}
% Ema Donev: emadonev@icloud.com


\begin{abstract}
We analyzed the incidence and properties of RR Lyrae stars that show evidence for amplitude and
phase modulation (the so-called Blazhko Effect) in a sample of $\sim$3,000 stars with LINEAR and ZTF light
curve data collected during the periods of 2002-2008 and 2018-2023, respectively. A preliminary subsample
of about $\sim$500 stars was algorithmically pre-selected using various data quality and light curve statistics,
and then 228 stars were confirmed visually as displaying the Blazhko effect. This sample increases the number
of field RR Lyrae stars displaying the Blazhko effect by more than 50\% and places a lower
limit of (11.4$\pm$0.8)\% for their incidence rate. We find that ab type RR Lyrae that show the Blazhko effect have
about 5\% (0.030 day) shorter periods than starting sample, a 7.1$\sigma$ statistically significant
difference. We find no significant differences in their light curve amplitudes and apparent magnitude (essentially,
signal-to-noise ratio) distributions. No period or other differences are found for c type RR Lyrae. We find convincing
examples of stars where the Blazhko effect can appear and disappear on time scales of several years.  With
time-resolved photometry expected from LSST, a similar analysis will be performed for even larger samples of field
RR Lyrae stars in the southern sky and we anticipate a higher fraction of discovered Blazhko stars due to better
sampling and superior photometric quality.
\end{abstract}
\keywords{Variable stars --- RR Lyrae variable stars --- Blazhko effect}
 

\input{intro.tex}
\input{analysis.tex}
\input{results}
\input{discussion}


\begin{acknowledgements}
We thank Mathew Graham for providing {\it ztfquery} code example to
us, and Robert Szab{\'o} for expert comments that improved presentation. 

\v{Z}.I. acknowledges funding by the Fulbright Foundation and thanks the Ru\d er Bo\v{s}kovi\'{c} Institute (Zagreb, Croatia) for hospitality.

This material is based on work supported in part by the
National Science Foundation through Cooperative Agreement
1258333 managed by the Association of Universities for
Research in Astronomy (AURA), and the Department of
Energy under Contract No. DE-AC02-76SF00515 with the
SLAC National Accelerator Laboratory. Additional LSST
funding comes from private donations, grants to universities,
and in-kind support from LSSTC Institutional Members. This
research has made use of NASA’s Astrophysics Data System
Bibliographic Services.

Based on observations obtained with the Samuel Oschin Telescope 48-inch and the 60-inch Telescope at the Palomar Observatory as part of the Zwicky Transient Facility project. ZTF is supported by the National Science Foundation under Grants No. AST-1440341 and AST-2034437 and a 
collaboration including current partners Caltech, IPAC, the Weizmann Institute of Science, the Oskar Klein Center at Stockholm University, the University of Maryland, Deutsches Elektronen-Synchrotron and Humboldt University, the TANGO Consortium of Taiwan, the University of Wisconsin at Milwaukee, Trinity College Dublin, Lawrence Livermore National Laboratories, IN2P3, University of Warwick, Ruhr University Bochum, Northwestern University and former partners the University of Washington, Los Alamos National Laboratories, and Lawrence Berkeley National Laboratories. Operations are conducted by COO, IPAC, and UW.

The LINEAR program is funded by the National Aeronautics and Space Administration at MIT Lincoln Laboratory under Air Force Contract FA8721-05-C-0002.
Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
\end{acknowledgements}

\software{Astropy \citep{2018AJ....156..123A, astropy:2022},
         Matplotlib \citep{matplotlib2007},
         SciPy \citep{scipy2020}, 
         astroML \citep{2012cidu.conf...47V}}

%\vspace{5mm}
%\facilities{LINEAR, Zwicky Transient Factory}
%\software{Astropy \citep{astropy:2013, astropy:2018, astropy:2022}, Matplotlib \citep{matplotlib2007}, SciPy \citep{scipy2020} }

\appendix

Table 1: The first 10 confirmed Blazhko stars with their LINEAR
IDs in the first column and then, for both LINEAR and ZTF, their
computed  light curve periods (day),
the number of data points per light curve, robust and ordinary $\chi^2$ values, and light curve amplitudes, followed by amplitude 
difference between LINEAR and ZTF, the strength and period of Blazhko peaks in their periodograms, light curve type (1: ab, 2: c), detection
significance flag for the periodograms (Z, L or ``-'' for no detection; the strength and period of Blazhko
peaks are not reliable when ``-'' ) and the selection score (see Sections 3.1 and 3.2 for details). The full table is available in online edition.


%\input{be_full.tex}
% only the first 10 entries from be_full.tex
\input{be_small.tex}


\bibliographystyle{aasjournal} % style aa.bst
\bibliography{paper} % your references Yourfile.bib
\end{document}

 